Review of Assigned Readings

### 2017-12-26 paper/paper.tex
delete redundant latex files
change location of date on paper title page

\documentclass[a4paper,american,12pt]{article}
\usepackage{graphicx}
\graphicspath{ {images/} }

@@

% Specify bibliography package
\usepackage{csquotes}% Recommended
\usepackage[style=apa,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

@@

    \begin{document}
    \begin{titlepage}
        \centering
        {\scshape\LARGE University of St.Gallen \\ \large School of Management, Economics, Law, Social Schiences and International Affairs \par}
        \vspace{2cm}
        {\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
		\vspace{1.5cm}        
        {\large\today\par}
        \vspace{1.5cm}
        {\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
        \vspace{1.5cm}
        {\itshape\large Alen Stepic - XX-XXX-XXX \\Chi Xu - XX-XXX-XXX \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - XX-XXX-XX \par}

        \begin{spacing}{1.5}
        \vspace{1cm}
        {Fall Term 2017 \par}
        \vspace{1cm}
        Supervisor\\
        {Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par} 
        \end{spacing}
    \end{titlepage}

    \begin{abstract}
    \pagenumbering{Roman}
    \begin{spacing}{1.5}

  (Insert text)

    \end{spacing}

    \end{abstract}

    \clearpage
    \tableofcontents

    \clearpage

    \listoffigures

    \clearpage

\begin{spacing}{1.2}
\cleardoublepage\pagenumbering{arabic}
\section{Section 1}

\subsection{Subsection 1}

\end{spacing}
\clearpage

\printbibliography

>>>>

\documentclass[a4paper,american,12pt]{article}
\usepackage{graphicx}
\graphicspath{{images/}}

@@

% Specify bibliography package
\usepackage{csquotes}
\usepackage[style=apa,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{references.bib}

@@

\begin{document}

    \begin{titlepage}
    \centering
    {\scshape\LARGE University of St.Gallen \\ \large School of Management, Economics, Law, Social Schiences and International Affairs \par}
    \vspace{2.0cm}
    {\huge\bfseries The effect of Twitter activity on Bitcoin price fluctuation  \par}
	\vspace{2.0cm}
    {\scshape\Large Software Engineering for Economists \\(7,610,1.00) \par}
    \vspace{2.0cm}
    {\itshape\large Alen Stepic - XX-XXX-XXX \\Chi Xu - XX-XXX-XXX \\Dimitrios Koumnakes - 10-613-370 \\Joël Sonderegger - 11-495-488 \\Severin Kranz - XX-XXX-XX \par}
    	\begin{spacing}{1}
    	\vspace{1.2cm}
    	{Fall Term 2017 \par}
    	\vspace{1.2cm}
    	Supervisor:\\
    	{Prof. Dr. Philipp Zahn\\ FGN HSG\\ Varnbüelstrasse 19\\ 9000 St. Gallen \par} 
    	\end{spacing}
	\vfill
	{\large \today\par}
    \end{titlepage}

    \begin{abstract}
    \pagenumbering{Roman}
    	\begin{spacing}{1.5}
    	(Insert text)
    	\end{spacing}
    \end{abstract}

\clearpage
\tableofcontents
\clearpage

	\begin{spacing}{1.2}
	\cleardoublepage\pagenumbering{arabic}
		\section{Research Question}
		\clearpage
		\section{Brief Background and Data Collection}
		\clearpage
		\section{Econometric Modelling and Results}
		\clearpage
		\section{Conclusion}
	\end{spacing}

\clearpage
\printbibliography
